Supporting Information

### 2018-02-26 SupportingInformation.Rmd
trivial changes
fill in nonparametric stat section

---
title: "Supporting Information"
author: "Shyamolina Ghosh and Daniel Reuman"
date: "February 12, 2018"
output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
---
updated on `r Sys.Date()`

@@

<!--Setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE)
seed<-101
families<-c(1,3:10,13,14,16:20)
source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
```

@@

Plot the raw data:
```{r load_data_Loecke, echo=F}
#Load your data - should be a data frame with 2 columns. Can contain NAs.
d<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d<-d[,c("SOCstock100","TSNstock100")]
plot(d[,1],d[,2],type="p",col="red",xlab="Soil C",ylab="Soil N",cex.lab=1)
rect(0,0,1,1)
```

Copula plot of the data:
```{r rankandplot_Loecke, echo=F}
#convert to a copula and plot
v<-getcopula(d=d,rankon=T,ploton=T) #with real data, rankon should be T
```

@@

The test of indepedence gave $p=$`r BivMS_res_Loecke$IndepTestRes`. We fitted several copulas
and got AIC values and upper- and lower-tail dependency estimates based on the fitted copulas:

```{r echo=F}
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
rownames(h)<-NULL
h
```

This shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data.

@@

@@

```{r vivj_matrix, echo=F}
# Select any two location pair [i,j] for a copula of species sp
# This function gives you a matrix with vi and vj as two columns
vivj_matrix<-function(d_allsp,sp,i,j){

  ds1<-d_allsp[[sp]][[i]]
  ds2<-d_allsp[[sp]][[j]]
  #----------------------------
  a1<-ds1$Year[1]
  a2<-ds2$Year[1]
  a3<-ds1$Year[dim(ds1)[1]]
  a4<-ds2$Year[dim(ds2)[1]]
  year_s<-max(a1,a2)
  year_e<-min(a3,a4)
  ind_s1<-which(ds1$Year==year_s)
  ind_s2<-which(ds2$Year==year_s)
  ind_e1<-which(ds1$Year==year_e)
  ind_e2<-which(ds2$Year==year_e)
  ds1<-ds1[ind_s1:ind_e1,]
  ds2<-ds2[ind_s2:ind_e2,]
  # Omitting the years and data containing NA in either d1 or d2 
  #from both d1 and d2
  if(anyNA(ds1$Dat)==T | anyNA(ds2$Dat)==T){
    ind_na1<-which(is.na(ds1$Dat))
    ind_na2<-c(ind_na1,which(is.na(ds2$Dat)))
    ind_na<-unique(ind_na2)

    d1Dat<-ds1$Dat[-ind_na]
    d2Dat<-ds2$Dat[-ind_na]
    Years<-ds1$Year[-ind_na]
    d1<-data.frame(Year=Years,Dat=d1Dat)
    d2<-data.frame(Year=Years,Dat=d2Dat)
  } else {
    d1<-ds1
    d2<-ds2
  }
  #get ranks modified now
  vi<-pobs(d1$Dat)
  vj<-pobs(d2$Dat)
  Years<-d1$Year
  #-------------------------
  #n_datapt<-length(vi)
  #--------------------
  #plot(vi,vj,type="p")
  #-------------------------
  mat<-as.matrix(cbind(vi,vj))
  return(mat)  
}
```

```{r d_allsp_data_aphid, echo=F}
d_allsp_data<-function(d0){

  name.aphid<-c("Apple-grass aphid","Bird cherry-oat aphid","Black bean aphid", "Blackberry-cereal aphid","Blackcurrant-sowthistle aphid",
                "Corn leaf aphid","Currant-lettuce aphid","Damson-hop aphid","Grain aphid","Green spruce aphid",
                "Leaf-curling plum aphid","Mealy cabbage aphid","Mealy plum aphid","Pea aphid","Peach-potato aphid",
                "Potato aphid","Rose-grain aphid","Shallot aphid","Sycamore aphid","Willow-carrot aphid")
  longs<-c(-4.567,0.57,-3.069,-3.312,-2.637,-1.682,-2.763,-0.356,-3.454,0.427,0.939)
  lats<-c(55.477,52.26,56.457,55.949,52.125,55.213,53.854,51.807,50.628,51.733,51.185)
  loc_name<-c("Ayr","Broom's Barn","Dundee","Edinburgh","Hereford","Newcastle","Preston","Rothamsted",
              "Starcross","Writtle","Wye")
  d0[d0==-999]<-NA
  Years<-1976:2010
  d_allsp<-list() #this is a list with 20 elements, all the species
  for (sp_c in 1:20)
  {
    d_thissp<-list() #a list with 11 locations for the current species
    for (st_c in 1:11)
    {
      d_thissp[[st_c]]<-data.frame(Year=Years,Dat=d0[st_c,((sp_c-1)*35+1):(sp_c*35)])
    }
    d_allsp[[sp_c]]<-d_thissp
  }
  names(d_allsp)<-name.aphid

  return(d_allsp=d_allsp)

}

# Aphid raw data for count
d0_count<-as.matrix(read.csv("Data/Aphid_data/APHID_DATA_RAW/aphidtscount141117.csv",header=F))

# Aphid raw data for first flight
d0_firstflight<-as.matrix(read.csv("Data/Aphid_data/APHID_DATA_RAW/aphidtsfirstflight141117.csv",header=F))

# Aphid raw data for flight duration
d0_flightduration<-as.matrix(read.csv("Data/Aphid_data/APHID_DATA_RAW/aphidtsflightduration141117.csv",header=F))

@@

```{r aphid_count, echo=F, cache=T, cache.extra=list(seed,d0_count)}
set.seed(seed)
cat(paste("start-time: ",Sys.time(),"\n"))
RES_aphid_count<-RES_single_sp(d_allsp=d_allsp_data(d0_count),sp=10,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
cat(paste("stop-time: ",Sys.time(),"\n"))
resloc<-"Results/"
saveRDS(RES_aphid_count,paste(resloc,file="AphidCopulaFit_selecloc_count_species_10.RDS",sep=""))
```

```{r}
RES_aphid_count
#no of locations showing greater lower tail dependence
sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)>0,na.rm=T)

#no of locations showing greater upper tail dependence
sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)<0,na.rm=T)

@@

@@

```{r aphid_firstflight, echo=F, cache=T, cache.extra=list(seed,d0_firstflight)}
set.seed(seed)
cat(paste("start-time: ",Sys.time(),"\n"))
RES_aphid_firstflight<-RES_single_sp(d_allsp=d_allsp_data(d0_firstflight),sp=11,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
cat(paste("stop-time: ",Sys.time(),"\n"))
resloc<-"Results/"
saveRDS(RES_aphid_firstflight,paste(resloc,file="AphidCopulaFit_selecloc_firstflight_species_11.RDS",sep=""))
```

```{r}
RES_aphid_firstflight
#no of locations showing greater lower tail dependence
sum((RES_aphid_firstflight$LTdep_AICw-RES_aphid_firstflight$UTdep_AICw)>0,na.rm=T)

#no of locations showing greater upper tail dependence
sum((RES_aphid_firstflight$LTdep_AICw-RES_aphid_firstflight$UTdep_AICw)<0,na.rm=T)

@@

Cout results

@@

```{r d_allsp_data_plankton_north_sea, echo=F}
d_allsp_data_plankton_north_sea<-function(d0){

  name.plankton<-c('Calanus_I-IV','Para-Pseudocalanus_spp','Temora_longicornis','Acartia_spp_(unidentified)','Centropages_typicus',
                   'Oithona_spp','Echinoderm_larvae','Calanus_finmarchicus','Calanus_helgolandicus','Metridia_lucens','Decapoda_larvae_(Total)',
                   'Euphausiacea_Total','Thalassiosira_spp','Rhizosolenia_styliformis','Ceratium_fusus','Ceratium_furca','Ceratium_tripos',
                   'Ceratium_macroceros','Rhizosolenia_alata_alata','Pseudocalanus_elongatus_Adult','Nitzschia_delicatissima','Nitzschia_seriata')

  longs<-read.csv("Data/Plankton_North_Sea_data/boxcornerlongs201117.csv",header=F)
  lats<-read.csv("Data/Plankton_North_Sea_data/boxcornerlats201117.csv",header=F)
  longs<-longs[[1]]
  lats<-lats[[1]]
  d0[d0==-999]<-NA
  Years<-1958:2013

  d_allsp<-list() #this is a list with 20 elements, all the species
  for (sp_c in 1:22)
  {
    d_thissp<-list() #a list with 11 locations for the current species
    d1<-d0[((sp_c-1)*26+1):(sp_c*26),]
    for (st_c in 1:26)
    {
      d_thissp[[st_c]]<-data.frame(Year=Years,Dat=d1[st_c,])
    }
    d_allsp[[sp_c]]<-d_thissp
  }
  names(d_allsp)<-name.plankton

  return(d_allsp=d_allsp)

}

d0_plankton_north_sea<-as.matrix(read.csv("Data/Plankton_North_Sea_data/planktontimeseries201117_4.csv",header=F))

```{r plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,d0_plankton_north_sea)}
set.seed(seed)
cat(paste("start-time: ",Sys.time(),"\n"))
RES_plankton_north_sea<-RES_single_sp(d_allsp=d_allsp_data_plankton_north_sea(d0_plankton_north_sea),sp=16,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=45)
cat(paste("stop-time: ",Sys.time(),"\n"))
resloc<-"Results/"
saveRDS(RES_plankton_north_sea,paste(resloc,file="Plankton_North_Sea_CopulaFit_selecloc_species_16.RDS",sep=""))
```

```{r}
RES_plankton_north_sea
#no of locations showing greater lower tail dependence
sum((RES_plankton_north_sea$LTdep_AICw-RES_plankton_north_sea$UTdep_AICw)>0,na.rm=T)

#no of locations showing greater upper tail dependence
sum((RES_plankton_north_sea$LTdep_AICw-RES_plankton_north_sea$UTdep_AICw)<0,na.rm=T)

# Question 2 analyses for each dataset

# Question 3 analyses for each dataset

>>>>

---
output:
  pdf_document: default
---
---
title: "Supporting Information"
author: "Shyamolina Ghosh and Daniel Reuman"
date: "February 12, 2018"
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.8cm"

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
---
updated on `r Sys.Date()`

```{r ,echo=FALSE}
library(captioner)
table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix="Figure")
```

@@

<!--Setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
families<-c(1,3:10,13,14,16:20)
source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
```

@@

```{r load_data_Loecke, echo=F, fig.cap="plot of the raw data", fig.height=5, fig.width=5}
#Load your data - should be a data frame with 2 columns. Can contain NAs.
d<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d<-d[,c("SOCstock100","TSNstock100")]
fig_nums("soilCNraw",display=F)
plot(d[,1],d[,2],type="p",col="red",xlab="Soil C",ylab="Soil N",cex.lab=1)
rect(0,0,1,1)
```

```{r rankandplot_Loecke, echo=F, fig.cap="Copula plot of soil C/N data",  fig.height=5, fig.width=5}
#convert to a copula and plot
fig_nums("soilCNcop",display=F)
v<-getcopula(d=d,rankon=T,ploton=T) #with real data, rankon should be T
```

@@

The test of indepedence gave *p=*`r BivMS_res_Loecke$IndepTestRes` . We fitted several copulas
and got AIC values and upper- and lower-tail dependency estimates based on the fitted copulas:

```{r soilCNfit,echo=F}
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
#rownames(h)<-NULL
table_nums("soilCNfit",display=F)
knitr::kable(h, caption = "Fitting info for soilC/N dataset")
```

`r table_nums("soilCNfit",display="c")` shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data.

@@

```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v)}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_soilCN/"

stat_soilCN<-copsync(v)
saveRDS(stat_soilCN,paste(resloc,file="stat_soilCN.RDS",sep=''))
sCN<-stat_soilCN[c(2:5,7,8,10:13)]
stat<-unlist(sCN)
```

```{r table_stat_soilCN, echo=F, results="asis"}
table_nums("table_stat_soilCN",display=F)

knitr::kable(data.frame(stat=stat),caption = "Non-parametric stats on soil C/N dataset")
```

```{r ,echo=F}
#sCN
CorlmCoru<-stat_soilCN$Corl-stat_soilCN$Coru
cat("Corl-Coru = ",CorlmCoru,"\n")
PlmPu<-stat_soilCN$Pl-stat_soilCN$Pu
cat("Pl-Pu = ",PlmPu,"\n")
TlmTu<-stat_soilCN$Tl-stat_soilCN$Tu
cat("Tl-Tu = ",TlmTu,"\n")
D2umD2l<-stat_soilCN$D2u-stat_soilCN$D2l
cat("D2u-D2l = ",D2umD2l,"\n")
```

@@

```{r read_aphid_data, echo=F}
# Aphid raw data for count
d0_count<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidtscount141117.csv",header=F))
data_aphid_count<-d_allsp_data(d0_count)

# Aphid raw data for first flight
d0_firstflight<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidtsfirstflight141117.csv",header=F))
data_aphid_ff<-d_allsp_data(d0_firstflight)

# Aphid raw data for flight duration   
#d0_flightduration<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidtsflightduration141117.csv",header=F))

@@

```{r RES_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count)}
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_aphid_count<-RES_single_sp(d_allsp=data_aphid_count,sp=10,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
#cat(paste("stop-time: ",Sys.time(),"\n"))
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_count,paste(resloc,file="AphidCopulaFit_selecloc_count_species_10.RDS",sep=""))
```

```{r read_RES_aphid_count, echo=F}
RES_aphid_count<-readRDS("./Results/fitting_results/AphidCopulaFit_selecloc_count_species_10.RDS")
```

```{r count_bestcop,echo=F,results="asis"}
#library(pander)
#pander(best_cop_LTdep, caption = "Hello caption!")
#knitr::kable(RES_aphid_count$info_ord_copname[,,1],format="latex",longtable=F,caption = "Aphid_count : Best fit copula family for each selective location pair")

table_nums("count_bestcop",display=F)
knitr::kable(RES_aphid_count$info_ord_copname[,,1],caption = "Aphid_count : Best fit copula family for each selective location pair")
```

```{r count_AICw,echo=F,results="asis"}

cat("\n\n\\pagebreak\n")

table_nums("count_AICw",display=F)
knitr::kable(RES_aphid_count$info_ord_AICw[,,1], caption = "Aphid_count : AICw for best fit copula family for each selective location pair")
```

```{r count_LTdep,echo=F,results="asis"}
table_nums("count_LTdep",display=F)
knitr::kable(RES_aphid_count$info_ord_LTdep[,,1], caption = "Aphid_count : Lower Tail dependence for best fit copula family for each selective location pair")
```

```{r count_UTdep,echo=F,results="asis"}
table_nums("count_UTdep",display=F)
knitr::kable(RES_aphid_count$info_ord_UTdep[,,1], caption = "Aphid_count : Upper Tail dependence for best fit copula family for each selective location pair")
```

```{r count_LTdep_AICw,echo=F,results="asis"}
table_nums("count_LTdep_AICw",display=F)
knitr::kable(RES_aphid_count$LTdep_AICw,caption = "Aphid_count : Lower Tail dependence statistic for best fit copula family for each selective location pair")
```

```{r count_UTdep_AICw,echo=F,results="asis"}
table_nums("count_UTdep_AICw",display=F)
knitr::kable(RES_aphid_count$UTdep_AICw,caption = "Aphid_count : Upper Tail dependence statistic for best fit copula family for each selective location pair")

@@

```{r count_LTmUT,echo=F,results="asis"}
table_nums("count_LTmUT",display=F)
knitr::kable(round(RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw,5),caption = "Aphid_count : Lower Tail - Upper Tail dependence statistic for best fit copula family for each of the selective location pair")
```

```{r count_p_CvM,echo=F,results="asis"}
table_nums("count_p_CvM",display=F)
knitr::kable(RES_aphid_count$gfc_p_CvM, caption = "Aphid_count : p-values (Cramer-von Mises-based test) for lowest AIC based best fit copula")
```

```{r count_p_KS,echo=F,results="asis"}
table_nums("count_p_KS",display=F)
knitr::kable(RES_aphid_count$gfc_p_KS,caption = "Aphid_count : p-values (Kolmogorov-Smirnov-based test) for lowest AIC based best fit copula")
```

`r table_nums("count_bestcop",display="c")` shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data.
The model-averaged (using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistic are presented in `r table_nums("count_LTdep_AICw",display="c")` and `r table_nums("count_UTdep_AICw",display="c")` respectively, and these values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper) in `r table_nums("count_LTmUT",display="c")` indicates it is different from 0 for most of the locations, answering the third part of question 1.

These results do convincingly show non-Gaussian copula structure, having **`r sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)>0,na.rm=T)`** out of **`r (dim(RES_aphid_count$gfc_p_CvM)[1]^2-dim(RES_aphid_count$gfc_p_CvM)[1])-RES_aphid_count$num_indep_loc_pair`** location pair with greater lower tail dependence. Our fitting results are supported by the lowest-AIC copula *p*-value in the Cramer-von Mises-based test [`r table_nums("count_p_CvM",display="c")`] of the goodness of its fit, and in the Kolmogorov-Smirnov-based test [`r table_nums("count_p_KS",display="c")`] of the goodness of fit.

The next section looks at tail dependence in a non-parametric way.

@@

```{r RES_aphid_ff, echo=F, cache=T, cache.extra=list(seed,data_aphid_ff)} 
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n"))
RES_aphid_ff<-RES_single_sp(d_allsp=data_aphid_ff,sp=11,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
#cat(paste("stop-time: ",Sys.time(),"\n")) 
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_ff,paste(resloc,file="AphidCopulaFit_selecloc_firstflight_species_11.RDS",sep=""))
```

```{r read_RES_aphid_ff,echo=F}
RES_aphid_ff<-readRDS("./Results/fitting_results/AphidCopulaFit_selecloc_firstflight_species_11.RDS")
```

```{r ff_bestcop,echo=F,results="asis"}
table_nums("ff_bestcop",display=F)
knitr::kable(RES_aphid_ff$info_ord_copname[,,1], caption = "Aphid_firstflight : Best fit copula family for each selective location pair")
```

```{r ff_AICw,echo=F,results="asis"}
table_nums("ff_AICw",display=F)
knitr::kable(RES_aphid_ff$info_ord_AICw[,,1], caption = "Aphid_firstflight : AICw for best fit copula family for each selective location pair")
```

```{r ff_LTdep,echo=F,results="asis"}
cat("\n\n\\pagebreak\n")

table_nums("ff_LTdep",display=F)
knitr::kable(RES_aphid_ff$info_ord_LTdep[,,1], caption = "Aphid_firstflight : Lower Tail dependence for best fit copula family for each selective location pair")
```

```{r ff_UTdep,echo=F,results="asis"}
table_nums("ff_UTdep",display=F)
knitr::kable(RES_aphid_ff$info_ord_UTdep[,,1], caption = "Aphid_firstflight : Upper Tail dependence for best fit copula family for each selective location pair")
```

```{r ff_LTdep_AICw,echo=F,results="asis"}
table_nums("ff_LTdep_AICw",display=F)
knitr::kable(RES_aphid_ff$LTdep_AICw, caption = "Aphid_firstflight : Lower Tail dependence statistic for best fit copula family for each selective location pair")
```

```{r ff_UTdep_AICw,echo=F,results="asis"}
table_nums("ff_UTdep_AICw",display=F)
knitr::kable(RES_aphid_ff$UTdep_AICw, caption = "Aphid_firstflight : Upper Tail dependence statistic for best fit copula family for each selective location pair")
```

```{r ff_LTmUT,echo=F,results="asis"}
table_nums("ff_LTmUT",display=F)
knitr::kable(round(RES_aphid_ff$LTdep_AICw-RES_aphid_ff$UTdep_AICw,5), caption = "Aphid_firstflight : Lower Tail - Upper Tail dependence statistic for best fit copula family for each of the selective location pair")
```

```{r ff_p_CvM,echo=F,results="asis"}
table_nums("ff_p_CvM",display=F)
knitr::kable(RES_aphid_ff$gfc_p_CvM, caption = "Aphid_firstflight : p-values (Cramer-von Mises-based test) for lowest AIC based best fit copula")
```

```{r ff_p_KS,echo=F,results="asis"}
table_nums("ff_p_KS",display=F)
knitr::kable(RES_aphid_ff$gfc_p_KS, caption = "Aphid_firstflight : p-values (Kolmogorov-Smirnov-based test) for lowest AIC based best fit copula")
```

`r table_nums("ff_bestcop",display="c")`  shows that several copulas are much better supported than the Gaussian copula, answering the first part of question 1 for these data.
The model-averaged (using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistic are presented in `r table_nums("ff_LTdep_AICw",display="c")` and `r table_nums("ff_UTdep_AICw",display="c")` respectively, and these values are distinct from what a Gaussian copula would give (i.e., 0), answering the second part of question 1 for these data. Furthermore, the difference of these two quantities (lower minus upper) in `r table_nums("ff_LTmUT",display="c")` indicates it is different from 0 for most of the locations, answering the third part of question 1.

These results do convincingly show non-Gaussian copula structure, having **`r sum((RES_aphid_ff$LTdep_AICw-RES_aphid_ff$UTdep_AICw)<0,na.rm=T)`** out of **`r (dim(RES_aphid_ff$gfc_p_CvM)[1]^2-dim(RES_aphid_ff$gfc_p_CvM)[1])-RES_aphid_ff$num_indep_loc_pair`** location pair more upper tail dependence. Our fitting results are supported by the lowest-AIC copula *p*-value in the Cramer-von Mises-based test [`r table_nums("ff_p_CvM",display="c")`] of the goodness of its fit, and in the Kolmogorov-Smirnov-based test [`r table_nums("ff_p_KS",display="c")`] of the goodness of fit.

@@

# Count results
```{r stat_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count)}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_aphid_count/"

sp<-10
good_loc <- good_loclist(d_allsp=data_aphid_count,sp=sp,data_pt_thrs=30)
longs<-c(-4.567,0.57,-3.069,-3.312,-2.637,-1.682,-2.763,-0.356,-3.454,0.427,0.939)
lats<-c(55.477,52.26,56.457,55.949,52.125,55.213,53.854,51.807,50.628,51.733,51.185)

stat_aphid_count<-multcall(d_allsp=data_aphid_count,sp=sp,lats=lats,longs=longs,pfname=paste(resloc,"Sp_",sp,sep=''),good_loc=good_loc)
saveRDS(stat_aphid_count,paste(resloc,file="stat_aphid_count_sp_10.RDS",sep='')) 
```

```{r read_stat_aphid_count,echo=F}
stat_aphid_count<-readRDS("./Results/stat_results/stat_aphid_count/stat_aphid_count_sp_10.RDS")
```

```{r count_resamp,echo=F,results="asis"}
table_nums("count_resamp",display=F)
knitr::kable(stat_aphid_count$numericdf, caption = "Aphid_count : resampling result for stat indicating lower tail dependence")
```

```{r count_allcop,echo=F}
fig_nums("count_allcop",display=F)
```
![copula plot for aphid-count](./Results/stat_results/stat_aphid_count/Sp_10_AllCops.pdf)

```{r count_spear,echo=F}
fig_nums("count_spear",display=F)
```
![Plot for aphid-count : Spearman vs. Distance](./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf)

```{r count_kend,echo=F}
fig_nums("count_kend",display=F)
```
![Plot for aphid-count : Kendall vs. Distance](./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf)

```{r count_Corl-Coru,echo=F}
fig_nums("count_Corl-Coru",display=F)
```
![Corl-Coru vs. Distance plot for aphid-count showing lower tail dependence](./Results/stat_results/stat_aphid_count/Sp_10_Corl-Coru_vs_D.pdf)

```{r count_Pl-Pu,echo=F}
fig_nums("count_Pl-Pu",display=F)
```
![Pl-Pu vs. Distance plot for aphid-count showing lower tail dependence](./Results/stat_results/stat_aphid_count/Sp_10_Pl-Pu_vs_D.pdf)

```{r count_Tl-Tu,echo=F}
fig_nums("count_Tl-Tu",display=F)
```
![Tl-Tu vs. Distance plot for aphid-count showing lower tail dependence](./Results/stat_results/stat_aphid_count/Sp_10_Tl-Tu_vs_D.pdf)

```{r count_D2u-D2l,echo=F}
fig_nums("count_D2u-D2l",display=F)
```
![D2u-D2l vs. Distance plot for aphid-count showing lower tail dependence](./Results/stat_results/stat_aphid_count/Sp_10_D2u-D2l_vs_D.pdf)

```{r count_D2u/D2l,echo=F}
fig_nums("count_D2u/D2l",display=F)
```
![D2u/D2l vs. Distance plot for aphid-count showing lower tail dependence](./Results/stat_results/stat_aphid_count/Sp_10_D2u_by_D2l_vs_D.pdf)

<!--
```{r, echo=F,out.width = "8cm", out.height= "8cm", out.caption="adhjk"}
knitr::include_graphics("./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf")
knitr::include_graphics("./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf")
```
-->

# First flight results

```{r stat_aphid_ff, echo=F, cache=T, cache.extra=list(seed,data_aphid_ff)}
set.seed(seed)
resloc<-"./Results/stat_results/stat_aphid_ff/"

sp<-11
good_loc<-good_loclist(d_allsp=data_aphid_ff,sp=sp,data_pt_thrs=30)
longs<-c(-4.567,0.57,-3.069,-3.312,-2.637,-1.682,-2.763,-0.356,-3.454,0.427,0.939)
lats<-c(55.477,52.26,56.457,55.949,52.125,55.213,53.854,51.807,50.628,51.733,51.185)

stat_aphid_ff<-multcall(d_allsp=data_aphid_ff,sp=sp,lats=lats,longs=longs,pfname=paste(resloc,"Sp_",sp,sep=''),good_loc=good_loc) 
saveRDS(stat_aphid_ff,paste(resloc,file="stat_aphid_ff_sp_11.RDS",sep='')) 
```

```{r read_stat_aphid_ff,echo=F}
stat_aphid_ff<-readRDS("./Results/stat_results/stat_aphid_ff/stat_aphid_ff_sp_11.RDS")
```

```{r ff_resamp,echo=F,results="asis"}
table_nums("ff_resamp",display=F)
knitr::kable(stat_aphid_ff$numericdf, caption = "Aphid_firstflight : resampling result for stat indicating upper tail dependence")
```

```{r ff_allcop,echo=F}
fig_nums("ff_allcop",display=F)
```
![copula plot for aphid-firstflight](./Results/stat_results/stat_aphid_ff/Sp_11_AllCops.pdf)

```{r ff_spear,echo=F}
fig_nums("ff_spear",display=F)
```
![Plot for aphid-firstflight : Spearman vs. Distance](./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf)

```{r ff_kend,echo=F}
fig_nums("ff_kend",display=F)
```
![Plot for aphid-firstflight : Kendall vs. Distance](./Results/stat_results/stat_aphid_ff/Sp_11_Kendall_vs_D.pdf)

```{r ff_Corl-Coru,echo=F}
fig_nums("ff_Corl-Coru",display=F)
```
![Corl-Coru vs. Distance plot for aphid-firstflight showing upper tail dependence](./Results/stat_results/stat_aphid_ff/Sp_11_Corl-Coru_vs_D.pdf)

```{r ff_Pl-Pu,echo=F}
fig_nums("ff_Pl-Pu",display=F)
```
![Pl-Pu vs. Distance plot for aphid-firstflight showing upper tail dependence](./Results/stat_results/stat_aphid_ff/Sp_11_Pl-Pu_vs_D.pdf)

```{r ff_Tl-Tu,echo=F}
fig_nums("ff_Tl-Tu",display=F)
```
![Tl-Tu vs. Distance plot for aphid-firstflight showing upper tail dependence](./Results/stat_results/stat_aphid_ff/Sp_11_Tl-Tu_vs_D.pdf)

```{r ff_D2u-D2l,echo=F}
fig_nums("ff_D2u-D2l",display=F)
```
![D2u-D2l vs. Distance plot for aphid-firstflight showing upper tail dependence](./Results/stat_results/stat_aphid_ff/Sp_11_D2u-D2l_vs_D.pdf)

```{r ff_D2u/D2l,echo=F}
fig_nums("ff_D2u/D2l",display=F)
```
![D2u/D2l vs. Distance plot for aphid-firstflight showing upper tail dependence](./Results/stat_results/stat_aphid_ff/Sp_11_D2u_by_D2l_vs_D.pdf)

@@

```{r read_plankton_north_sea_data, echo=F}
d0_plankton_north_sea<-as.matrix(read.csv("./Data/Plankton_North_Sea_data/planktontimeseries201117_4.csv",header=F))
data_plankton_north_sea<-d_allsp_data_plankton_north_sea(d0_plankton_north_sea)
```

```{r RES_plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea)}
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_plankton_north_sea<-RES_single_sp(d_allsp=data_plankton_north_sea,sp=16,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=45)
#cat(paste("stop-time: ",Sys.time(),"\n"))    
resloc<-"./Results/fitting_results/"
saveRDS(RES_plankton_north_sea,paste(resloc,file="Plankton_North_Sea_CopulaFit_selecloc_species_16.RDS",sep=""))
```

```{r read_RES_plankton_north_sea,echo=F}
RES_plankton_north_sea<-readRDS("./Results/fitting_results/Plankton_North_Sea_CopulaFit_selecloc_species_16.RDS")
```

```{r pns_bestcop,echo=F,results="asis"}
#library(pander)
#pander(best_cop_LTdep, caption = "Hello caption!")
# alternatively,
#pandoc.table(RES_plankton_north_sea$info_ord_AICw[,,1], caption="Plankton_north_sea : AICw for best fit copula family for each selective location pair")
cat("\n\n\\pagebreak\n")

table_nums("pns_bestcop",display=F)
knitr::kable(RES_plankton_north_sea$info_ord_copname[,,1], caption = "Plankton_north_sea : Best fit copula family for each selective location pair")
```

```{r pns_AICw,echo=F,results="asis"}
table_nums("pns_AICw",display=F)
knitr::kable(round(RES_plankton_north_sea$info_ord_AICw[,,1],3), caption = "Plankton_north_sea : AICw for best fit copula family for each selective location pair")
```

```{r pns_LTdep,echo=F,results="asis"}
cat("\n\n\\pagebreak\n")

table_nums("pns_LTdep",display=F)
knitr::kable(round(RES_plankton_north_sea$info_ord_LTdep[,,1],3), caption = "Plankton_north_sea : Lower Tail dependence for best fit copula family for each selective location pair")
```

```{r pns_UTdep,echo=F,results="asis"}
table_nums("pns_UTdep",display=F)
knitr::kable(round(RES_plankton_north_sea$info_ord_UTdep[,,1],3), caption = "Plankton_north_sea : Upper Tail dependence for best fit copula family for each selective location pair")
```

```{r pns_LTdep_AICw,echo=F,results="asis"}
cat("\n\n\\pagebreak\n")

table_nums("pns_LTdep_AICw",display=F)
knitr::kable(round(RES_plankton_north_sea$LTdep_AICw,3), caption = "Plankton_north_sea : Lower Tail dependence statistic for best fit copula family for each selective location pair")
```

```{r pns_UTdep_AICw,echo=F,results="asis"}
table_nums("pns_UTdep_AICw",display=F)
knitr::kable(round(RES_plankton_north_sea$UTdep_AICw,3), caption = "Plankton_north_sea : Upper Tail dependence statistic for best fit copula family for each selective location pair")
```

```{r pns_LTmUT,echo=F,results="asis"}
cat("\n\n\\pagebreak\n")

table_nums("pns_LTmUT",display=F)
knitr::kable(round(RES_plankton_north_sea$LTdep_AICw-RES_plankton_north_sea$UTdep_AICw,3), caption = "Plankton_north_sea : Lower Tail - Upper Tail dependence statistic for best fit copula family for each of the selective location pair")
```

```{r pns_p_CvM,echo=F,results="asis"}
table_nums("pns_p_CvM",display=F)
knitr::kable(round(RES_plankton_north_sea$gfc_p_CvM,3), caption = "Plankton_north_sea : p-values (Cramer-von Mises-based test) for lowest AIC based best fit copula")
```

```{r pns_p_KS,echo=F,results="asis"}
cat("\n\n\\pagebreak\n")

table_nums("pns_p_KS",display=F)
knitr::kable(round(RES_plankton_north_sea$gfc_p_KS,3), caption = "Plankton_north_sea : p-values (Kolmogorov-Smirnov-based test) for lowest AIC based best fit copula")
```
